Switch equivalence and weak prime domains for fusions

### 2023-10-27 fusione.tex
pulizia

 %(query-replace-regexp "\\\\sqsubseteq^{sh}_{\\([^}]*\\)}" "\\\\shiftpre[\\1]")
% --- LNCS ---'
\documentclass{llncs}

@@

%from pawel
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
%2 righe tolte da Fabio
\usepackage{amssymb}
%\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{xspace}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{cite}
\usepackage{float}
\usepackage{fancybox}

@@

\spnewtheorem*{notation}{Notation}{\bfseries}{\rmfamily}

@@

@@

\section{Introduction}

@@

The following proposition establishes a key property of Van Kampen squares with a mono as a side: they are not only pushouts, but also pullbacks.
\begin{proposition}\label{prop:pbpo} Let $m\colon A\to C$ be a monomorphism in a category $\X$. Then every Van Kampen square
	\[\xymatrix{A\ar[r]^{g} \ar[d]_{m} & B \ar[d]^{n} \\ C \ar[r]_{f}  & D}\]
	is also a pullback square and $n$ is a monomorphism.
\end{proposition}
\begin{proof} Take the following cube:
	\[\xymatrix@C=13pt@R=13pt{&A\ar[dd]|\hole_(.65){\id{A}}\ar[rr]^{g} \ar[dl]_{\id{A}} && B \ar[dd]^{\id{B}} \ar[dl]_{\id{B}} \\ A  \ar[dd]_{m}\ar[rr]^(.65){g} & & B \ar[dd]_(.3){n}\\&A\ar[rr]|\hole^(.65){g} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{f} & & D}\]
	By construction the top face of the cube is a pushout and the back one a pullback. The left face is a pullback because $m$ is mono. Thus the Van Kampen property yields that the front and the right faces are pullbacks and the thesis follows. \qed 
\end{proof}

@@

	\smallskip \noindent 
	$(\Leftarrow)$ Let $h:C\to A$ be such that $c=m\circ h$. By the Van Kampen property the top face of the given cube is a pushout. Thus the dotted $k:D'\to B$ in the following diagram exists.
		\[\xymatrix@C=40pt{A' \ar@/^.3cm/[ddr]^(.8){a} \ar[d]_{m'} \ar[r]^{f'} & B' \ar[d]^{n'} \ar@/^.3cm/[ddr]^{b} \\  C' \ar@/_.3cm/[dr]_{h} \ar[r]_{g'}|(.7)\hole & D' \ar@{.>}[dr]^{k}\\ &A \ar[r]_f& B }\]
	The thesis now follows at once. \qed 
\end{proof}

@@

\begin{proof} We can begin noticinng that $g$, being the pullback of the monomorphism $k$, is monic too. Thus we can build the cube below, in which all the vertical faces are pullbacks.
	\[\xymatrix@C=20pt@R=10pt{ & &X\ar[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar[ddd]_{g} \ar[rrr]^{b}&&& B\ar[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar[dl]_{f}&&& A \ar[dl]^{h}\\ & Y  \ar[dl]_{g}&&& B \ar[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
	By hypothesis the face is a stable pushout and so its top one is a pushout. \Cref{lem:po1} now entails that the right half of the rectangle with which we have started is a pushout too. \qed 
\end{proof}

@@

From \Cref{prop:pbpoad}, in turn, we can derive the following corollaries.
\begin{corollary}\label{cor:rego}
	In a $\mathcal{M}$-adhesive category $\X$, every $m\in\mathcal{M}$ is a regular mono.
\end{corollary}
\begin{proof}
Let $m$ be an element of $\mathcal{M}$ and consider its pushout along itself.
\[\xymatrix{X\ar[r]^m \ar[d]_m& Y\ar[d]^{f}\\Y \ar[r]_g & Z}\]
By \Cref{prop:pbpoad} this square is a pullback, proving that $m$ is the equalizer of the arrows $f,g\colon Y\rightrightarrows Z$. \qed 
\end{proof}

@@

	Using \Cref{lem:po1}, it is enough to show that the left half of the original rectangle is a pushout. We can build the same cube of the previous point:
	\[\xymatrix@C=20pt@R=10pt{ & &X\ar[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar[ddd]_{g} \ar[rrr]^{b}&&& B\ar[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar[dl]_{f}&&& A \ar[dl]^{h}\\ & Y \ar[rrr]|(.67)\hole^{b} \ar[dl]_{g}&&& B \ar[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
	Its vertical faces are all pullbacks, those the top one is a pushout and we can conclude. \qed 
\end{enumerate}
\end{proof}

@@

	Now, in both cubes the front and left faces are pullbacks, thus, by \Cref{lem:pb1}, their back face is a pullback too. Since $m\leq m$, \Cref{lem:varie} now entails that $k_1\leq k_2$ and $k_2\leq k_1$. Thus there exists an isomorphism $f:W_1\circ W_2$ such that $k_1=k_2\circ f$. To see that $h_2=f\circ h_1$, we can compute:
	\begin{align*}
		k_2\circ f \circ h_1 & = k_1\circ h_1\\&= n\circ m\\&= k_2\circ h_2
	\end{align*}
	The claim now follows since $k_2$ is a monomoprhism. \qed 
\end{proof}

@@

\begin{remark}
	If $\X$ is not a small category , then $\gpo$ has a proper class of vertices.
\end{remark}

	We can spell out more explicitly what  a derivation $\dder{D}$ between $G$ and $H$ is.  $\dder{D}$ is a, possibly empty, sequence $\{\dder{D}_i\}_{i=0}^n$ of direct derivations such that:
	\begin{enumerate}
		\item for every index $i$, $\dder{D}_i$ is a direct derivation $G_i \Mapsto G_{i+1}$;
		\item $G_0=G$ and $G_{n+1}=H$.
	\end{enumerate}

@@

	Moreover,  if $\mathcal{D}_i$ is an application of the rule $\rho_i\in R$, then we can define an associated sequence of rules as $r(\der{D})$ as $\{\rho_i\}_{i=0}^n$.

@@

\begin{definition}
	The \emph{DPO-derivation category} $\dpo$ of a left-linear DPO-rewriting system $(\X, \R)$ is the free category on $\gpo$.
\end{definition}
\begin{remark}
Derivations, being paths in a graph, can be concatenate: given $\der{D}=\{\dder{D}\}_{i=0}^n$ between $G$ and $H$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^m$, their \emph{concatenation} $\der{D}\cdot\der{D}'$ is the derivation $\{\dder{E}_i\}_{i=0}^{m+n+1}$ in which
\[\dder{E}_i:=\begin{cases}
	\dder{D}_i & i \leq n\\
	\dder{D}'_{i-(n+1)} & n< i 
\end{cases}\]

It is immediate to see that the concatenation of two non-empty derivations coincides with their composition in $\dpo$. 
\end{remark}

@@

\begin{proposition}\label{prop:ske}
	Every category $\X$ has a skeleton. 
\end{proposition}
\begin{proof}
	For every object $X\in \X$, pick a single representative $\pi(X)$ of its isomorphism class. Let $\ske$ be the full subcategory given by these objects. By definition $\ske$ is skeletal and the inclusion functor is full, faithful and essentially surjective.\qed 
\end{proof}
\begin{remark}
	The proof of \Cref{prop:ske} relies on the axiom of choice for classes.
	\end{remark}
\begin{remark}
	It is possible to proof that every two skeleta of a given category $\X$ are isomorphic (not only equivalent). For the remaining of this paper we assume that a skeleton $\ske$ of $\X$ and a functor $\pi:\X\to \ske$ are chosen once and for all.
\end{remark}

@@

@@

Similarly, if $\hat{m}_0:\hat{L}_0\to E, \hat{m}'_0:L'_0\to E'$ the matches of $\der{E}_0$, $\der{E}'_0$, we can consider the diagram
\[\xymatrix@C=40pt@R=10pt{ &&&\hat{R}_0\ar[dddr]^{\hat{h}'_0} \ar[dddl]_{\hat{h}_0}|(.67)\hole\\&&\hat{K}_0 \ar[dl]_{\hat{l}_0} \ar[ur]^{\hat{r}_0}\ar[dddr]^{k'_0} \ar[dddl]_{\hat{k}_0}|(.67)\hole\\&\hat{L}_n\ar[dddr]^(.4){\hat{m}'_0} \ar[dddl]_(.4){\hat{m}_0}\\&&\hat{G}_1 \ar[rr]^{\varphi^0_3} && \hat{G}'_1\\ & \hat{D}_0 \ar[ur]_(.7){\hat{g}_0} \ar[rr]^{\varphi^0_2} \ar[dl]_{\hat{f}_0}&& \hat{D}'_0 \ar[ur]_{\hat{g}'_0}\ar[dl]^{\hat{f}'_0}\\ E \ar[rr]_{\varphi^0_1} && E'}\]
and computing we get
\begin{align*}
	\id{\pi(E)}\circ \alpha^{-1} \circ \hat{m}_0&=(\alpha')^{-1}\circ \varphi^0_1 \circ \alpha \circ \alpha^{-1} \circ \hat{m}_0\\&=(\alpha')^{-1}\circ \varphi^0_1  \circ \hat{m}_0\\&=(\alpha')^{-1}\circ \hat{m}'_n
\end{align*}
together with
\begin{align*} \id{\pi(E)}\circ \alpha^{-1}\circ \hat{f}_0  &=(\alpha')^{-1}\circ \varphi^0_1 \circ \alpha \circ \alpha^{-1}\circ \hat{f}_0\\&=(\alpha')^{-1}\circ \varphi^0_1\circ \hat{f}_0\\&=(\alpha')^{-1}\circ \hat{f}'_0\circ \varphi^0_2\end{align*}
The previous two identities show that $\psi^{n+1}$ is an abstract equivalence between $\dder{E}_0$ and $\dder{E}'_0$. By hypothesis $\pi(H)=\pi(E)$ and, moreover, we have
	\[\begin{split}
		\psi^{0}_1\circ \alpha &= \phi^0_1\circ \alpha \\&= \alpha'
	\end{split}\qquad \begin{split}
	\psi^{n+m-1}_3\circ \xi &=\varphi^m_3\circ \xi \\&= \xi'
	\end{split}\]
Therefore the thesis now follows.	\qed 
\end{proof}

@@

	To see that such $c$ is unique, suppose that $c':\tpro{D}\to C$ is given such that
	\[c'\circ p_1=b \qquad c'\circ p_2 = a\]
	Then, for every $X\in \Delta(\der{D})$ we have
	\begin{align*}
		c'\circ \iota_X &= \begin{cases}
			c'\circ p_1\circ \iota'_{X} & X\in \Delta(\der{D}')\\
			c'\circ p_2\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
			c'\circ \iota_{D_j} & X=D_j
		\end{cases}\\&=\begin{cases}
		b\circ \iota'_{X} & X\in \Delta(\der{D}')\\
		a\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
		c'\circ p_1 \circ \iota'_{G_j} \circ f_j  & X=D_j
		\end{cases}\\&= \begin{cases}
		b\circ \iota'_{X} & X\in \Delta(\der{D}')\\
		a\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
			b\circ \iota'_{G_j} \circ f_j  & X=D_j
		\end{cases}\\&=c_X\\&=c\circ \iota_X
	\end{align*}
	allowing us to deduce that $c'=c$.	\qed 	
	\end{enumerate}
\end{proof}
\begin{corollary}\label{cor:ele}
	Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ be a derivation between $G$ and $H$. Let $j$ and $k$ be two indexes less or equal than $n+1$ and suppose that $j< k$.  Consider two arrows $a:T\to G_j$, $b:T\to G_k$. If $\iota_{G_j}\circ a = \iota_{G_k}\circ b$, 
	then  there exist arrow $c:T\to D_j $  such that \[f_j\circ c = a\qquad \iota_{D_j}\circ c =\iota_{G_k}\circ b\]
	\end{corollary}
\begin{proof} We split the cases.
	\begin{itemize}
		\item $j=0$. Consider $\der{D}_1:=\{\dder{D}_0\}$ and $\der{D}_2:=\{\dder{D}_i\}_{i=1}^n$.  Consider the diagram below in which, by \Cref{rem:zero}, the rectangle on the bottom right is a pushout.
		\[\xymatrix@C= 40pt{T  \ar@/_.6cm/[ddd]_{a}\ar@{.>}[d]^{t}\ar[rr]^{b}&& G_k \ar[d]_{\iota_{2, G_k}} \ar@/^.6cm/[ddd]^{\iota_{G_k}}\\D_{0} \ar[r]^{g_0}\ar[d]^{f_0}& G_{1} \ar[r]^-{\iota_{2,G_{1}}} & \lpro \der{D}_2\rpro \ar[dd]_{p_2} \\ G \ar[drr]^{\iota_G} \ar[d]^{\iota_{1,G}}\\ \lpro \der{D}_1 \rpro \ar[rr]_{p_1}  &&\tpro{D} }\] 
		Since $f_0$ and $\iota_{1,G}$ are in $\mathcal{M}$ the same rectangle is an $\mathcal{M}$-pushout and so, by \Cref{prop:pbpoad} is a pullback and the thesis follows.
		\item   $j\neq 0$. We proceed as in the point above. Using point $4$ of \Cref{lem:colim} we know that the bottom right rectangle in the diagram below is a pushout. 
			\[\xymatrix@C=30pt{T  \ar@/_.6cm/[ddd]_{a}\ar@{.>}[d]^{t}\ar[rr]^{b}&& G_k \ar[d]_{\iota_{2, G_k}} \ar@/^.6cm/[ddd]^{\iota_{G_k}}\\D_{j} \ar[r]^{g_j}\ar[d]^{f_j}& G_{j+1} \ar[r]^-{\hat{\iota}_{G_{j+1}}} & \lpro \der{\hat{D}}\rpro \ar[dd]_{p_2} \\ G_j \ar[d]^{\iota'_{G_j}} \ar[drr]^{\iota_{G_j}}\\ \lpro \der{D}' \rpro \ar[rr]_{p_1}  &&\tpro{D} }\] 
		Point $2$ of \Cref{lem:colim} entails that $\iota'_{G_j}$ is in $\mathcal{M}$, and so is $f_j$ as it is the pushout of $l_j$. Thus the rectangle we are considering is an $\mathcal{M}$-pushout and the thesis follows again from \Cref{prop:pbpoad}. \qed
	\end{itemize}
\end{proof}

@@

\begin{proposition}\label{prop:sum}
\todo{il caso in cui sigma si decomponga come due permu}
\end{proposition}
\begin{proof}
	contenuto...\qed 
\end{proof}

@@

\begin{corollary}\label{cor:dec}
	\todo{prefisso e suffisso}
\end{corollary}
\begin{proof}
	contenuto...\qed 
\end{proof}

@@

\subsection{Sequentially independendent and switchable derivations}
\todo{A VERY NICE INTRO}

@@

Putting together the two diagrams above we get the thesis. \qed 
\end{proof}

@@

We can now prove some properties of switch equivalence.
\begin{lemma}\todo{Def. 3 della bozza di Andrea }Let $(\X, \R)$ be a left-linear DPO-rewriting system. Then the following hold true: 
	\begin{enumerate}
		\item 
		\item 
		\item 
		\item 
	\end{enumerate}
\end{lemma}
\begin{proof}\begin{enumerate}
		\item 
		\item 
		\item 
		\item \qed 
	\end{enumerate}
\end{proof}

@@

		\item \qed 
	\end{enumerate}
\end{proof}

 We need another lemma, similar to \Cref{lem:iig1}.
\begin{lemma}\label{lem:iig2}\todo{nell'altro senso}
\end{lemma}
\begin{proof}
 \todo{fare} \qed 
\end{proof}

@@

\begin{lemma}
	contenuto...
\end{lemma}
\begin{proof}
	contenuto...\qed 
\end{proof}

@@

\begin{theorem}
	\todo{filler e classe B+}
\end{theorem}
\begin{proof}\qed 
\end{proof}

@@

\begin{proposition}
	\todo{da B a B+}
\end{proposition}
\begin{proof}
	contenuto... \qed 
\end{proof}
\begin{lemma}\todo{due proprietà classe B}
\end{lemma}
\begin{proof}
	\qed 
\end{proof}

>>>>

 %(query-replace-regexp "\\\\sqsubseteq^{sh}_{\\([^}]*\\)}" "\\\\shiftpre[\\1]")
% --- LNCS ---'
\documentclass{article}

@@

%from pawel
\usepackage[latin1]{inputenc}
\usepackage{amsmath}

\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{xspace}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{cite}
\usepackage{float}
\usepackage{fancybox}

@@

%\spnewtheorem*{notation}{Notation}{\bfseries}{\rmfamily}

@@

%%%%% Ambienti matematici  %%%%%%
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem*{notation}{Notation}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

@@

\tableofcontents
\section{Introduction}

@@

The following proposition establishes a key property of Van Kampen squares with a mono as a side: they are not only pushouts, but also pullbacks.
\begin{proposition}\label{prop:pbpo} Let $m\colon A\to C$ be a monomorphism in a category $\X$. Then every Van Kampen square
	\[\xymatrix{A\ar[r]^{g} \ar[d]_{m} & B \ar[d]^{n} \\ C \ar[r]_{f}  & D}\]
	is also a pullback square and $n$ is a monomorphism.
\end{proposition}
\begin{proof} Take the following cube:
	\[\xymatrix@C=13pt@R=13pt{&A\ar[dd]|\hole_(.65){\id{A}}\ar[rr]^{g} \ar[dl]_{\id{A}} && B \ar[dd]^{\id{B}} \ar[dl]_{\id{B}} \\ A  \ar[dd]_{m}\ar[rr]^(.65){g} & & B \ar[dd]_(.3){n}\\&A\ar[rr]|\hole^(.65){g} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{f} & & D}\]
	By construction the top face of the cube is a pushout and the back one a pullback. The left face is a pullback because $m$ is mono. Thus the Van Kampen property yields that the front and the right faces are pullbacks and the thesis follows. \qedhere 
\end{proof}

@@

	\smallskip \noindent 
	$(\Leftarrow)$ Let $h:C\to A$ be such that $c=m\circ h$. By the Van Kampen property the top face of the given cube is a pushout. Thus the dotted $k:D'\to B$ in the following diagram exists.
		\[\xymatrix@C=40pt{A' \ar@/^.3cm/[ddr]^(.8){a} \ar[d]_{m'} \ar[r]^{f'} & B' \ar[d]^{n'} \ar@/^.3cm/[ddr]^{b} \\  C' \ar@/_.3cm/[dr]_{h} \ar[r]_{g'}|(.7)\hole & D' \ar@{.>}[dr]^{k}\\ &A \ar[r]_f& B }\]
	The thesis now follows at once. \qedhere 
\end{proof}

@@

\begin{proof} We can begin noticinng that $g$, being the pullback of the monomorphism $k$, is monic too. Thus we can build the cube below, in which all the vertical faces are pullbacks.
	\[\xymatrix@C=20pt@R=10pt{ & &X\ar[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar[ddd]_{g} \ar[rrr]^{b}&&& B\ar[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar[dl]_{f}&&& A \ar[dl]^{h}\\ & Y  \ar[dl]_{g}&&& B \ar[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
	By hypothesis the face is a stable pushout and so its top one is a pushout. \Cref{lem:po1} now entails that the right half of the rectangle with which we have started is a pushout too. \qedhere 
\end{proof}

@@

From \Cref{prop:pbpoad}, in turn, we can derive the following corollaries.
\begin{corollary}\label{cor:rego}
	In a $\mathcal{M}$-adhesive category $\X$, every $m\in\mathcal{M}$ is a regular mono.
\end{corollary}
\begin{proof}
Let $m$ be an element of $\mathcal{M}$ and consider its pushout along itself.
\[\xymatrix{X\ar[r]^m \ar[d]_m& Y\ar[d]^{f}\\Y \ar[r]_g & Z}\]
By \Cref{prop:pbpoad} this square is a pullback, proving that $m$ is the equalizer of the arrows $f,g\colon Y\rightrightarrows Z$. \qedhere 
\end{proof}

@@

	Using \Cref{lem:po1}, it is enough to show that the left half of the original rectangle is a pushout. We can build the same cube of the previous point:
	\[\xymatrix@C=20pt@R=10pt{ & &X\ar[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar[ddd]_{g} \ar[rrr]^{b}&&& B\ar[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar[dl]_{f}&&& A \ar[dl]^{h}\\ & Y \ar[rrr]|(.67)\hole^{b} \ar[dl]_{g}&&& B \ar[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
	Its vertical faces are all pullbacks, those the top one is a pushout and we can conclude. \qedhere 
\end{enumerate}
\end{proof}

@@

	Now, in both cubes the front and left faces are pullbacks, thus, by \Cref{lem:pb1}, their back face is a pullback too. Since $m\leq m$, \Cref{lem:varie} now entails that $k_1\leq k_2$ and $k_2\leq k_1$. Thus there exists an isomorphism $f:W_1\circ W_2$ such that $k_1=k_2\circ f$. To see that $h_2=f\circ h_1$, we can compute:
	\begin{align*}
		k_2\circ f \circ h_1 & = k_1\circ h_1\\&= n\circ m\\&= k_2\circ h_2
	\end{align*}
	The claim now follows since $k_2$ is a monomoprhism. \qedhere 
\end{proof}

@@

\begin{remark}
We can spell out more explicitly what  a derivation $\dder{D}$ betwee nis.  An \emph{empty derivation} starting and ending in $G$ is just $G$ itself.  A \emph{non-empty derivation} $\dder{D}$ is a sequence $\{\dder{D}_i\}_{i=0}^n$ of direct derivations such that:
\begin{enumerate}
	\item for every index $i$, $\dder{D}_i$ is a direct derivation $G_i \Mapsto G_{i+1}$;
	\item $G_0=G$ and $G_{n+1}=H$.
\end{enumerate}

@@

Moreover,  if every $\dder{D}_i$ applies the rule $\rho_i\in R$, then we can define an associated sequence of rules as $r(\der{D})$ as $\{\rho_i\}_{i=0}^n$.
\end{remark}

@@

\begin{definition}
	The \emph{DPO-derivation category} $\dpo$ of a left-linear DPO-rewriting system $(\X, \R)$ is the category in which arrows between $G$ and $H$ are given by, possibly empty, derivations. Composition is concatenation of paths in $\gpo$ and identities are given by empty derivations.
\end{definition} 	
\begin{remark}
	More explicitly, given $\der{D}=\{\dder{D}\}_{i=0}^n$ between $G$ and $H$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^m$, their concatenation $\der{D}\cdot\der{D}'$ is the derivation $\{\dder{E}_i\}_{i=0}^{m+n+1}$ in which
	\[\dder{E}_i:=\begin{cases}
		\dder{D}_i & i \leq n\\
		\dder{D}'_{i-(n+1)} & n< i 
	\end{cases}\]	
\end{remark}

@@

\begin{proposition}\label{prop:ske}
	Every category $\X$ has a skeleton. 
\end{proposition}
\begin{proof}
	For every object $X\in \X$, pick a single representative $\pi(X)$ of its isomorphism class. Let $\ske$ be the full subcategory given by these objects. By definition $\ske$ is skeletal and the inclusion functor is full, faithful and essentially surjective.\qedhere 
\end{proof}
\begin{remark}
	The proof of \Cref{prop:ske} relies on the axiom of choice for classes.
	\end{remark}
\begin{remark}
	It is possible to proof that every two skeleta of a given category $\X$ are isomorphic (not only equivalent). For the remaining of this paper we assume that a skeleton $\ske$ of $\X$ and a functor $\pi:\X\to \ske$ are chosen once and for all.
\end{remark}

@@

\begin{remark}A decorated derivation $(\der{D}, \alpha, \omega)$ with $\der{D}$ empty is just a span
	\[\xymatrix{G & \pi(G) \ar[r]^{\omega} \ar[l]_{\alpha} & G}\]
	in which both $\omega$ and $\alpha$ are isomorphisms.
\end{remark}

@@

Similarly, if $\hat{m}_0:\hat{L}_0\to E, \hat{m}'_0:L'_0\to E'$ the matches of $\der{E}_0$, $\der{E}'_0$, we can consider the diagram
\[\xymatrix@C=40pt@R=10pt{ &&&\hat{R}_0\ar[dddr]^{\hat{h}'_0} \ar[dddl]_{\hat{h}_0}|(.67)\hole\\&&\hat{K}_0 \ar[dl]_{\hat{l}_0} \ar[ur]^{\hat{r}_0}\ar[dddr]^{k'_0} \ar[dddl]_{\hat{k}_0}|(.67)\hole\\&\hat{L}_n\ar[dddr]^(.4){\hat{m}'_0} \ar[dddl]_(.4){\hat{m}_0}\\&&\hat{G}_1 \ar[rr]^{\varphi^0_3} && \hat{G}'_1\\ & \hat{D}_0 \ar[ur]_(.7){\hat{g}_0} \ar[rr]^{\varphi^0_2} \ar[dl]_{\hat{f}_0}&& \hat{D}'_0 \ar[ur]_{\hat{g}'_0}\ar[dl]^{\hat{f}'_0}\\ E \ar[rr]_{\varphi^0_1} && E'}\]
and computing we get
\begin{align*}
	\id{\pi(E)}\circ \alpha^{-1} \circ \hat{m}_0&=(\alpha')^{-1}\circ \varphi^0_1 \circ \alpha \circ \alpha^{-1} \circ \hat{m}_0\\&=(\alpha')^{-1}\circ \varphi^0_1  \circ \hat{m}_0\\&=(\alpha')^{-1}\circ \hat{m}'_n
\end{align*}
together with
\begin{align*} \id{\pi(E)}\circ \alpha^{-1}\circ \hat{f}_0  &=(\alpha')^{-1}\circ \varphi^0_1 \circ \alpha \circ \alpha^{-1}\circ \hat{f}_0\\&=(\alpha')^{-1}\circ \varphi^0_1\circ \hat{f}_0\\&=(\alpha')^{-1}\circ \hat{f}'_0\circ \varphi^0_2\end{align*}
The previous two identities show that $\psi^{n+1}$ is an abstract equivalence between $\dder{E}_0$ and $\dder{E}'_0$. By hypothesis $\pi(H)=\pi(E)$ and, moreover, we have
	\[\begin{split}
		\psi^{0}_1\circ \alpha &= \phi^0_1\circ \alpha \\&= \alpha'
	\end{split}\qquad \begin{split}
	\psi^{n+m-1}_3\circ \xi &=\varphi^m_3\circ \xi \\&= \xi'
	\end{split}\]
Therefore the thesis now follows.	\qedhere 
\end{proof}

@@

	To see that such $c$ is unique, suppose that $c':\tpro{D}\to C$ is given such that
	\[c'\circ p_1=b \qquad c'\circ p_2 = a\]
	Then, for every $X\in \Delta(\der{D})$ we have
	\begin{align*}
		c'\circ \iota_X &= \begin{cases}
			c'\circ p_1\circ \iota'_{X} & X\in \Delta(\der{D}')\\
			c'\circ p_2\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
			c'\circ \iota_{D_j} & X=D_j
		\end{cases}\\&=\begin{cases}
		b\circ \iota'_{X} & X\in \Delta(\der{D}')\\
		a\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
		c'\circ p_1 \circ \iota'_{G_j} \circ f_j  & X=D_j
		\end{cases}\\&= \begin{cases}
		b\circ \iota'_{X} & X\in \Delta(\der{D}')\\
		a\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
			b\circ \iota'_{G_j} \circ f_j  & X=D_j
		\end{cases}\\&=c_X\\&=c\circ \iota_X
	\end{align*}
	allowing us to deduce that $c'=c$. \qedhere 
	\end{enumerate}
\end{proof}
\begin{corollary}\label{cor:ele}
	Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ be a derivation between $G$ and $H$. Let $j$ and $k$ be two indexes less or equal than $n+1$ and suppose that $j< k$.  Consider two arrows $a:T\to G_j$, $b:T\to G_k$. If $\iota_{G_j}\circ a = \iota_{G_k}\circ b$, 
	then  there exist arrow $c:T\to D_j $  such that \[f_j\circ c = a\qquad \iota_{D_j}\circ c =\iota_{G_k}\circ b\]
	\end{corollary}
\begin{proof} We split the cases.
	\begin{itemize}
		\item $j=0$. Consider $\der{D}_1:=\{\dder{D}_0\}$ and $\der{D}_2:=\{\dder{D}_i\}_{i=1}^n$.  Consider the diagram below in which, by \Cref{rem:zero}, the rectangle on the bottom right is a pushout.
		\[\xymatrix@C= 40pt{T  \ar@/_.6cm/[ddd]_{a}\ar@{.>}[d]^{t}\ar[rr]^{b}&& G_k \ar[d]_{\iota_{2, G_k}} \ar@/^.6cm/[ddd]^{\iota_{G_k}}\\D_{0} \ar[r]^{g_0}\ar[d]^{f_0}& G_{1} \ar[r]^-{\iota_{2,G_{1}}} & \lpro \der{D}_2\rpro \ar[dd]_{p_2} \\ G \ar[drr]^{\iota_G} \ar[d]^{\iota_{1,G}}\\ \lpro \der{D}_1 \rpro \ar[rr]_{p_1}  &&\tpro{D} }\] 
		Since $f_0$ and $\iota_{1,G}$ are in $\mathcal{M}$ the same rectangle is an $\mathcal{M}$-pushout and so, by \Cref{prop:pbpoad} is a pullback and the thesis follows.
		\item   $j\neq 0$. We proceed as in the point above. Using point $4$ of \Cref{lem:colim} we know that the bottom right rectangle in the diagram below is a pushout. 
			\[\xymatrix@C=30pt{T  \ar@/_.6cm/[ddd]_{a}\ar@{.>}[d]^{t}\ar[rr]^{b}&& G_k \ar[d]_{\iota_{2, G_k}} \ar@/^.6cm/[ddd]^{\iota_{G_k}}\\D_{j} \ar[r]^{g_j}\ar[d]^{f_j}& G_{j+1} \ar[r]^-{\hat{\iota}_{G_{j+1}}} & \lpro \der{\hat{D}}\rpro \ar[dd]_{p_2} \\ G_j \ar[d]^{\iota'_{G_j}} \ar[drr]^{\iota_{G_j}}\\ \lpro \der{D}' \rpro \ar[rr]_{p_1}  &&\tpro{D} }\] 
		Point $2$ of \Cref{lem:colim} entails that $\iota'_{G_j}$ is in $\mathcal{M}$, and so is $f_j$ as it is the pushout of $l_j$. Thus the rectangle we are considering is an $\mathcal{M}$-pushout and the thesis follows again from \Cref{prop:pbpoad}. \qedhere
	\end{itemize}
\end{proof}

@@

\begin{proposition}\label{prop:sum}
\todo{il caso in cui sigma si decomponga come due permu}
\end{proposition}
\begin{proof}
	contenuto...\qedhere 
\end{proof}

@@

\begin{corollary}\label{cor:dec}
	\todo{prefisso e suffisso}
\end{corollary}
\begin{proof}
	contenuto...\qedhere 
\end{proof}

@@

\subsection{Sequentially independent and switchable derivations}
\todo{A VERY NICE INTRO}

@@

Putting together the two diagrams above we get the thesis. \qedhere 
\end{proof}

@@

We can now prove some properties of switch equivalence.
\begin{lemma}\todo{Def. 3 della bozza di Andrea }Let $(\X, \R)$ be a left-linear DPO-rewriting system. Then the following hold true: 
	\begin{enumerate}
		\item 
		\item 
		\item 
		\item 
	\end{enumerate}
\end{lemma}
\begin{proof}\begin{enumerate}
		\item 
		\item 
		\item 
		\item \qedhere 
	\end{enumerate}
\end{proof}

@@

		\item \qedhere 
	\end{enumerate}
\end{proof}

 We need another lemma, similar to \Cref{lem:iig1}.
\begin{lemma}\label{lem:iig2}\todo{nell'altro senso}
\end{lemma}
\begin{proof}
 \todo{fare} \qedhere 
\end{proof}

@@

\begin{lemma}
	contenuto...
\end{lemma}
\begin{proof}
	contenuto...\qedhere 
\end{proof}

@@

\begin{theorem}
	\todo{filler e classe B+}
\end{theorem}
\begin{proof}\qedhere 
\end{proof}

@@

\begin{proposition}
	\todo{da B a B+}
\end{proposition}
\begin{proof}
	contenuto... \qedhere 
\end{proof}
\begin{lemma}\todo{due proprietà classe B}
\end{lemma}
\begin{proof}
	\qedhere 
\end{proof}
